Detailed Chemical Abundances with \tc

### 2015-09-08 article/ms.tex
Test hooks
Include git abbreviated hash, etc whoohoo

% Convenient colloquiualisms.
\newcommand\article{\textit Article}
\newcommand\tc{\textit{The Cannon} }

@@

\section*{Acknowledgments}
This research can be reproduced in full using the commands \texttt{pip install fireworks},
\texttt{fireworks-reproduce}. This article was produced using commit hash \texttt{hash}.

This research was fostered by discussions at the \textit{New Milky Way}
conference hosted by the Munich Institute for Astro- and Particle Physics, and
the \textit{Stellar Streams in the Local Universe} conference hosted at Ringberg
Castle by the Max-Planck-Institut F\"ur Astronomie. This research made use of 
Astropy, a community-developed core Python package for Astronomy \citep{astropy}.

@@

\section{Appendix A: Reproducing this research}
This article has been compiled from the `git` repository hosted online at GitHub (commit hash \gitHash on `master` branch). The figures and tables included in this article can be reproduced in full using the following commands in a modern terminal:

git clone git@github.com:andycasey/fireworks.git fireworks
cd fireworks
python setup.py install
python reproduce.py
cd article
make

If the required tools are not available on the readers system (e.g., `git`), this research can also be produced using the public Docker image .

>>>>

% Comment

% Convenient colloquiualisms.
\newcommand\article{\textit{Article}}
\newcommand\tc{\textit{The Cannon} }

@@

\section*{Acknowledgments}
This research was fostered by discussions at the \textit{New Milky Way}
conference hosted by the Munich Institute for Astro- and Particle Physics, and
the \textit{Stellar Streams in the Local Universe} conference hosted at Ringberg
Castle by the Max-Planck-Institut F\"ur Astronomie. This research made use of 
Astropy, a community-developed core Python package for Astronomy \citep{astropy}.

@@

\section{Appendix A: Reproducing this research}
This \article{} has been compiled from the \texttt{git} repository (commit hash \texttt{\gitAbbrevHash} on \texttt{\gitBranch} branch) hosted online at GitHub\footnote{https://www.github.com/andycasey/fireworks}. The complete data analysis, figures and tables included in this \article{} can be reproduced in full using the following commands in a modern Unix-based terminal:
\vspace{0.5em}

\noindent\texttt{[reproducibility commands]} 
\vspace{0.5em} \\
If the required tools are not available on the readers system (e.g., \texttt{git}), this research can also be produced using the public Docker image \texttt{[docker image reference]}.
